\sysfull

### 2018-08-06 paper/asplos19/coalescing.tex
change the style of algo 1
revisions to coalescing (not complete)

\sys's design includes a novel task scheduler that uses efficient,
energy-aware task coalescing to amortize static task overheads, and uses a timer-based
task-splitting mechanism to avoid non-termination of tasks too long
for a device's energy buffer. 
% 
\subsection{Task Coalescing}
\label{sec:task_coalescing}
% 
When a device's buffered energy is sufficient to run multiple consecutive tasks
without a power failure, committing state after each task is an unnecessary
overhead. \sys eliminates this overhead by coalescing a sequence of tasks and deferring the commit
operations for all tasks to the end of the sequence. 
In general, committing involves moving state manipulated by a task
into its permanent location in non-volatile memory.  In particular, \sys's
commit procedure copies dirty pages of memory that a task updated between fast,
volatile working memory and slower, non-volatile main memory; we defer the
details of paging privatization and commit to Section~\ref{sec:memory_virtulaization}.

Coalescing tasks brings a double benefit. First, coalescing reduces the total number of relatively
high-latency, high-energy non-volatile memory accesses because tasks primarily
access variables in relatively low-latency, low-energy volatile memory.
Second, coalescing eliminates the unnecessary instructions that implement task
commit, which our measurements in Section~\ref{sec:evaluation} show constitute
a substantial run-time overhead.

An effective colescing strategy must be {\em aggressive} enough, attempting to coalesce a
large number of tasks to amortize a large amount of commit overhead. However, it must also be 
{\em conservative} enough, attempting to coalesce only as many tasks as will execute
to completion given a certain energy conditions, reducing the risk or long coalesced task re-execution penalty.

% An effective coalescing strategy moderates the risk of a power failure during a
% long coalesced task and capitalizes on the benefits of deferred commits by
% adapting the target size of the dynamic task to the energy available at
% runtime. 
%
\begin{figure}{t}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	%
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$z$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
% \end{wrapfigure}
\end{figure}
% 
\subsection{Task Coalescing Strategies} 
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i$th task
executed since the last power failure. $H$ (history) is the total number of
tasks between the last executed task and the power failure that preceding it.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight $W$ is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

>>>>

\sys's design includes a novel task scheduler. It uses efficient, energy-aware task coalescing to amortize static task overheads, and a timer-based task-splitting mechanism to avoid non-termination of tasks too long for a device's energy buffer.

\subsection{Task Coalescing}
\label{sec:task_coalescing}

When a device's buffered energy is sufficient to run multiple consecutive tasks without a power failure, committing state after each task is an unnecessary overhead. \sys eliminates this overhead by coalescing a sequence of tasks and deferring the commit
operations for all tasks to the end of the sequence. In general, committing involves moving state manipulated by a task into its permanent location in non-volatile memory. In particular, \sys's commit procedure copies dirty pages of memory that a task updated between fast, volatile working memory and slower, non-volatile main memory; we defer the details of paging privatization and commit to Section~\ref{sec:memory_virtulaization}.

Coalescing has a double benefit. First, coalescing reduces the total number of relatively high-latency, high-energy non-volatile memory accesses because tasks primarily access variables in relatively low-latency, low-energy volatile memory. Second, coalescing eliminates the unnecessary instructions that implement task commit, which constitute a substantial run-time overhead, as our measurements in Section~\ref{sec:evaluation} show.

An effective coalescing strategy must be {\em aggressive} enough, attempting to coalesce a large number of tasks to amortize commit overhead. However, it must also be  {\em conservative} enough, attempting to coalesce only as many tasks as will execute to completion given a certain energy conditions, reducing the risk or long coalesced task re-execution penalty.

\begin{algorithm}[t]
	\caption{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$z$}
        \State $H \gets 0$ \Comment{\note{add comments for some lines to get rid of white spaces}}
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
% 
\subsection{Task Coalescing Strategies}

Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing strategy. In the algorithm, $B$ (target budget) is total number of static tasks that \sys will next attempt to coalesce. $T_\text{i}$ is the $i$th task
executed since the last power failure. $H$ (history) is the total number of
tasks between the last executed task and the power failure that preceding it.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight $W$ is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.
